---
title: "1. Course introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Course introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(intro.R)
```




The general structure of the course planned as:


## Day 1 (Day 2? )

* Basic R introduction
    + Data types
    + Control structures
    + Functions
    + Debugging

## Day 2

* Data manipulation, 
* Data cleaning, tidying

## Day 3 

  * Visualization with ggplot
  * Exploratory statistics
  
  
## Day 4

* Work with S4 objects 
    +  GRanges 
    + SummarizedExperiment
    + example data analysis (Gene expression)
    
## Day 5 

* Reproducible research
  + version control, git
  + RMarkdown
  + workflowr
* Good programming practice  





# Resources 


The following resources were used to prepare the slides and exercises:  

[LINK](https://bookdown.org/rdpeng/rprogdatascience/)

[LINK](https://r4ds.had.co.nz/)

[LINK](https://adv-r.hadley.nz/)

[LINK](https://www.r-exercises.com/start-here-to-learn-r/)





# Useful stuff





